The `zoon` R package for reproducible and shareable species distribution modelling

### 2016-03-21 ms.Rmd
Add paragraphs on lists.

Add something on lists!

>>>>

Many SDM analyses require running similar workflow in parallel. 
In applied settings this may be running the same analysis for multiple species.
In methodological work, it is important to compare new methods or models to benchmarks.
To divide a `zoon` workflow into multiple parallel analyses the `list` function is used.
`list` can be used to split the analysis at any point: listing multiple occurrence modules together will run the workflow on different occurrence datasets while listing multiple model modules will fit different models to a shared, identical dataset but then apply output modules to each model separately.

The complete workflow, with multiple modules defined with the `Chain` function and parallel analyses being defined with the `list` function can be visualised by calling `plot` with the workflow object as it's argument.
This displays the names of all modules and the broader structure of the workflow as well as displaying which modules are not available in the online repository (Figure ).
